Representation Learning for Generalized Planning - SAT Encodings

### 2020-09-07 doc/encodings/paper.tex
Optional constraints in CNF to force descending transitions to be selected as Good

>>>>

\smallpar{C3 (Optional)} All descending transitions must be considered Good:
\begin{align}
 V(s, d) \land V(s', d') \rightarrow Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
 Good(s, s'),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
\end{align}
